---
title: "Ratings Forecasting - Get Data"
date: "`r Sys.Date()`"
---

# Loading Packages and Data Load
## Setup Custom Functions
```{r setup, echo=FALSE, cache=FALSE}
source(here::here("/notebooks/Brazil_W25-54/00-Setup.R"))
```

## Load TXT Files to the envoriment and tidy data
```{r Load TXT Files}
# Load TXT Files to the envoriment ----
raw_path <- "./data_raw/15minBrazil/"
filenames <- list.files(
  path = raw_path,
  pattern = "*.*",
  recursive = TRUE
)
fullpath <- file.path(raw_path, filenames)

ratings_raw <- lapply(fullpath, data.table::fread,
  skip = 2, sep = ",", showProgress = FALSE,
  blank.lines.skip = TRUE, stringsAsFactors = FALSE,
  col.names = c("Channel", "Date", "Time", "Target", "TRP", "ABS")
)
data <- data.table::rbindlist(ratings_raw)

# Adjusting time (Data comes with a 30h day (06:00-29:59)
convert.to.sec <- function(X) {
  X <- strsplit(X, ":")
  sapply(X, function(Y) sum(as.numeric(Y) * c(3600, 60, 1)))
}

# Tidy Data ----
data <- data %>%
  tibble() %>%
  mutate(
    DateTime =
      fast_strptime(Date, "%Y-%m-%d", tz = "UTC", lt = FALSE) +
        seconds(convert.to.sec(data$Time)),
    Channel = as.factor(Channel),
    Target = as.factor(Target)
  ) %>%
  select(-Date, -Time)

rm(ratings_raw, filenames, fullpath, raw_path, convert.to.sec)
```

# Feature Engineering
## Getting some key aspects
```{r Setting Parameters}
DateStart <- min(data$DateTime)
DateEnd <- max(data$DateTime)
DateCutoff <- DateStart + hours(
  round(
    0.9 *
      time_length(lubridate::interval(DateStart, DateEnd), "hour"),
    0
  )
)
ForecastHorizon <- "6 months" # Used on final forecast
YearStart <- year(DateStart) # Used on Holidays Tsibble / data.frame
YearEnd <- year(DateEnd + as.duration(ForecastHorizon)) # Used on Holidays Tsibble / data.frame
```

## Holidays
I built the holidays dataset because:
# prophet::generated_holidays doesn't have the ecclesiastical holidays (based on Easter) for Brazil and Proclamation of Republic holiday is on Nov 5th and not on Nov 15. 
# bizdays:holidaysANBIMA doesn't have the name of the holidays, what prevent the creation of dummies for each holiday (effect of "Carnival Tuesday" might be different than the effect of "Christmas Day").
# timeDate::holiday doesn't have Brazil. I therefore used timeDate::Easter to se Carnival and Corpus Christi. 

I also use the weekdays to understand bridges of long weekends.

```{r Creating holiday}
# First on Prophet format
holidays_brazil_prophet <-
  tibble(ds = date(as.character()), weekday = integer(), holiday = as.character(), lower_window = integer(), upper_window = integer()) %>%
  add_row(ds = ymd(timeDate::Easter(YearStart:YearEnd, -2)), holiday = "Easter Friday") %>%
  add_row(ds = ymd(timeDate::Easter(YearStart:YearEnd, -48)), holiday = "Carnival Monday", lower_window = 0, upper_window = 0) %>%
  add_row(ds = ymd(timeDate::Easter(YearStart:YearEnd, -47)), holiday = "Carnival Tuesday", lower_window = 0, upper_window = 0) %>%
  add_row(ds = ymd(timeDate::Easter(YearStart:YearEnd, -46)), holiday = "Carnival Wednesday", lower_window = 0, upper_window = 0) %>%
  add_row(ds = ymd(timeDate::Easter(YearStart:YearEnd, 60)), holiday = "CorpusChristi") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-01-01")), ymd(paste0(YearEnd, "-01-01")), by = "years"), holiday = "New Year's Day") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-01-25")), ymd(paste0(YearEnd, "-01-25")), by = "years"), holiday = "Sao Paulo Anniversary") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-04-21")), ymd(paste0(YearEnd, "-04-21")), by = "years"), holiday = "Tiradentes") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-05-01")), ymd(paste0(YearEnd, "-05-01")), by = "years"), holiday = "Workers' Day") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-09-07")), ymd(paste0(YearEnd, "-09-07")), by = "years"), holiday = "Independece Day") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-10-12")), ymd(paste0(YearEnd, "-10-12")), by = "years"), holiday = "Our Lady of Apparition") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-11-02")), ymd(paste0(YearEnd, "-11-02")), by = "years"), holiday = "All Souls' Day") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-11-15")), ymd(paste0(YearEnd, "-11-15")), by = "years"), holiday = "Republic Day") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-11-20")), ymd(paste0(YearEnd, "-11-20")), by = "years"), holiday = "Black Awareness Day") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-12-24")), ymd(paste0(YearEnd, "-12-24")), by = "years"), holiday = "Christmas Eve") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-12-25")), ymd(paste0(YearEnd, "-12-25")), by = "years"), holiday = "Christmas Day") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-12-31")), ymd(paste0(YearEnd, "-12-31")), by = "years"), holiday = "New Year's Eve") %>%
  mutate(
    weekday = wday(ds),
    lower_window = ifelse(is.na(lower_window), ifelse(weekday == 3, -1, 0), lower_window),
    upper_window = ifelse(is.na(upper_window), ifelse(weekday == 5, 1, 0), upper_window)
  ) %>%
  arrange(ds)
```

```{r converting holidays to long format}
holidays_brazil <- holidays_brazil_prophet %>%
  dplyr::filter(lower_window != 0 | upper_window != 0) %>%
  mutate(
    ds = (ds + days(upper_window) + days(lower_window)),
    holiday = paste(holiday, " Bridge"),
    lower_window = 0,
    upper_window = 0
  ) %>%
  bind_rows(holidays_brazil_prophet, .) %>%
  select(ds, holiday) %>%
  rename(date = ds) %>%
  distinct(date, .keep_all = TRUE) %>%
  arrange(date) %>%
  mutate(date = as.Date(as.POSIXct(date)))
```

```{r incorporate holidays to data}
data <- data %>%
  mutate(date = date(DateTime)) %>%
  left_join(holidays_brazil, by = c("date" = "date")) %>%
  mutate(holidayflag = ifelse(is.na(holiday), 0, 1)) %>%
  select(-date)

holidays_brazil_prophet <- as_tsibble(holidays_brazil_prophet, index = ds)
```

## Other Features
Besides holidays, I'm activelly adding more variables to the model so we can have more elements to fit a Linear Model (GLM) or Neural Network.
```{r}
data <- data %>%
  tk_augment_timeseries_signature(.date_var = DateTime) %>%
  mutate(daytype = ifelse(wday == 1 | wday == 7, 0, 1)) %>%
  mutate(time = hms::hms(as.numeric(DateTime - floor_date(DateTime, "1 day"), unit = "secs")))
```

## Tsibble & Break Train & Test
```{r}
data_ts <- as_tsibble(data, index = DateTime, key = c("Channel", "Target"))
data_ts_train <- data_ts %>%
  filter_index(. ~ paste(DateCutoff))
data_ts_test <- data_ts %>%
  filter_index(paste(DateCutoff) ~ .)
```

## Future Data
```{r}
ChannelsTargets <- data %>%
  select(Target, Channel) %>%
  distinct(Target, Channel)

data_ts_future <-
  data.frame(DateTime = seq(from = DateEnd + as.duration("15 minutes"), to = DateEnd + as.period(ForecastHorizon), by = as.duration("15 minutes"))) %>%
  mutate(daytype = ifelse(wday(DateTime) == 1 | wday(DateTime) == 7, 0, 1)) %>%
  mutate(time = hms::hms(as.numeric(DateTime - floor_date(DateTime, "1 day"), unit = "secs"))) %>%
  mutate(date = date(DateTime)) %>%
  left_join(holidays_brazil, by = c("date" = "date")) %>%
  mutate(holidayflag = ifelse(is.na(holiday), 0, 1)) %>%
  select(-date) %>%
  tk_augment_timeseries_signature(.date_var = DateTime) %>%
  merge(ChannelsTargets) %>%
  as_tsibble(index = DateTime, key = c("Channel", "Target"))
```

## Save Dataset
```{r}
save(list = ls(all.names = TRUE), file=here::here("data/data.Rdata"))
```