---
title: "Ratings Forecasting"
date: "`r Sys.Date()`"
output:
  rmdformats::material:
    highlight: kate
---
# Loading Packages and Data Load
## Setup Custom Functions
```{r setup, echo=FALSE, cache=FALSE}
source(here::here("/notebooks/Brazil_W25-54/00-Setup.R"))
```

# Modeling Tests
## Prophet
```{r}
tictoc::tic()
fit_train_prophet <- data_ts_train %>%
  filter(Channel == "Discovery Channel") %>%
  model(
    pr1 = fable.prophet::prophet(log(ABS + 1) ~ month.lbl + season(period = 24*15) + season(period = 7*24*15) + holiday(holidays_brazil_prophet))
  )
tictoc::toc()

accuracy(fit_train_prophet)
```

Observa-se que o modelo mais completo, com dummies de mês, ajusta melhoAr que os modelos menos completos.

## Fasster
```{r}
future::plan("multiprocess")
tictoc::tic()
fit_train_fasster <- data_ts_train %>%
  filter(
    Channel == "Discovery Channel" # , DateTime >= DateStart + dyears(1)
  ) %>%
  model(
    fasster1 = fasster::FASSTER(log(ABS + 1) ~ trend(1) + fourier(96, 12) + holidayflag),
    fasster2 = fasster::FASSTER(log(ABS + 1) ~ factor(wday) %S% trend(1) + fourier(96, 6) + holidayflag),
    fasster3 = fasster::FASSTER(log(ABS + 1) ~ trend(2) + fourier(96, 6) + fourier(24 * 4 * 7, 6) + holidayflag)
  )
tictoc::toc()

accuracy(fit_train_fasster)
```

A Melhor performamce está no modelo simples,

## TSLM
```{r}
tictoc::tic()
fit_train_tslm <- data_ts_train %>%
  filter(Channel == "Discovery Channel") %>%
  model(
    tslm1 = TSLM(log(ABS + 1) ~ factor(year) + factor(holidayflag) + factor(wday) + factor(month) + factor(time)),
    tslm2 = TSLM(log(ABS + 1) ~ factor(year) + factor(holidayflag) + fourier("week", K = 6) + fourier("day", K = 6)),
  )
tictoc::toc()
accuracy(fit_train_tslm)
```

## Arima
```{r}
tictoc::tic()
fit_train_arima <- data_ts_train %>%
  filter(Channel == "Discovery Channel") %>%
  model(
    arima1 = ARIMA(log(ABS + 1) ~ factor(holidayflag)),
    arima2 = ARIMA(log(ABS + 1) ~ factor(wday) + factor(holidayflag)),
    arima3 = ARIMA(log(ABS + 1) ~ factor(holidayflag) + fourier("week", K = 6) + fourier("day", K = 6))
  )
tictoc::toc()
report(fit_train_arima)
accuracy(fit_train_arima)
```

## ETS
```{r}
tictoc::tic()
fit_train_ets <- data_ts_train %>%
  filter(Channel == "Discovery Channel") %>%
  model(
    ets1 = ETS(log(ABS + 1)),
    # ets2 = ETS(log(ABS + 1) ~ trend(method = c("A", "Ad")) + season(method = c("A", "M"), period = "1 day")) It doesn't work b/c ETS is limited to 24 obs/period and I have 96.
  )
tictoc::toc()
accuracy(fit_train_ets)
glimpse(fit_train_ets)
```
It clearly shows a over-fit issue. 
I'd like to try to run my own Excel ETS algorithm where I do a single model for each weekday. The terms (Alpha, Beta, Phi) are reached through a single log-likelihood function. In my Excel model, I use Solver.