---
title: "Ratings Forecasting"
date: "`r Sys.Date()`"
output:
  rmdformats::material:
    highlight: kate
---

# Loading Packages and Data Load
## Setup Custom Functions
```{r setup, echo=FALSE, cache=FALSE}

# Custom Functions
convert.to.sec <- function(X) {
  X <- strsplit(X, ":")
  sapply(X, function(Y) sum(as.numeric(Y) * c(3600, 60, 1)))
}

installpak <- function(pkg) {
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) {
    install.packages(new.pkg, dependencies = TRUE)
  }
}

# Load Packages
## Pacotes não dispníveis no CRAN - Instalação
#NonCRANPackages_b <- c("mitchelloharawild/fable.prophet", "tidyverts/fasster")
#remotes::install_github(NonCRANPackages_b)
#rm(NonCRANPackages_b)

## Pacores
RequiredPackages <- c( # Pacotes que uso, mas não quero carregar, chamo funções de maneira declarada
  "timeSeries" # Usado para criar o calendario (filho do fbasics da família Rmerics)
  , "data.table" # Uso o fread para importar e fundir as bases
  , "tictoc" # Controla o tempo
  , "remotes" # Instalação dos pacotes do Github
  , "future.apply"
) # Required for Prophet

LoadedPackages <- c(
  "tidyverse" # Life
  , "skimr",
  "future" # Parallel Processing


  # Calendar functions
  , "lubridate" # Dealing with time (ymd and others)
  , "timetk" # Exploratory

  # Modeling
  , "prophet"

  # Tidyverts
  , "tsibble",
  "fable",
  "feasts",
  "fabletools"

  # RMD
  , "knitr",
  "rmdformats"
)

NonCRANPackages <- c(
  "fable.prophet",
  "fasster"
)

installpak(c(RequiredPackages, LoadedPackages))
sapply(c(LoadedPackages, NonCRANPackages), require, character.only = TRUE)

# Global RMarkdown options
options(max.print = "75")
opts_chunk$set(
  echo = FALSE,
  cache = TRUE,
  prompt = FALSE,
  tidy = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE
)
opts_knit$set(width = 75)

# Environment Options
Sys.setenv("LANGUAGE" = "EN")
Sys.setlocale("LC_ALL", "en_US.UTF-8")

  rm(LoadedPackages, NonCRANPackages, RequiredPackages, installpak)

```

## Load TXT Files to the envoriment and tidy data
```{r}
# Load TXT Files to the envoriment ----
raw_path <- "../data_raw/15minBrazil/"
filenames <- list.files(
  path = raw_path,
  pattern = "*.*",
  recursive = TRUE
)
fullpath <- file.path(raw_path, filenames)

ratings_raw <- lapply(fullpath, data.table::fread,
  skip = 2, sep = ",", showProgress = FALSE,
  blank.lines.skip = TRUE, stringsAsFactors = FALSE,
  col.names = c("Channel", "Date", "Time", "Target", "TRP", "ABS")
)
data <- data.table::rbindlist(ratings_raw)

# Tidy Data ----
data <- data %>%
  tibble() %>%
  mutate(
    DateTime =
      fast_strptime(Date, "%Y-%m-%d", tz = "UTC", lt = FALSE) +
        seconds(convert.to.sec(data$Time)),
    Channel = as.factor(Channel),
    Target = as.factor(Target)
  ) %>%
  select(-Date, -Time)

rm(ratings_raw, filenames, fullpath, raw_path, convert.to.sec)
```

# Feature Engineering
## Getting some key aspects
```{r}
DateStart <- min(data$DateTime)
DateEnd <- max(data$DateTime)
DateCutoff <- DateStart + hours(
  round(
    0.9 *
      time_length(lubridate::interval(DateStart, DateEnd), "hour"),
    0
  )
)
ForecastHorizon <- "6 months" # Used on final forecast
YearStart <- year(DateStart) # Used on Holidays Tsibble / data.frame
YearEnd <- year(DateEnd + as.duration(ForecastHorizon)) # Used on Holidays Tsibble / data.frame
```

## Holidays
I built the holidays dataset because:
# prophet::generated_holidays doesn't have the ecclesiastical holidays (based on Easter) for Brazil and Proclamation of Republic holiday is on Nov 5th and not on Nov 15. 
# bizdays:holidaysANBIMA doesn't have the name of the holidays, what prevent the creation of dummies for each holiday (effect of "Carnival Tuesday" might be different than the effect of "Christmas Day").
# timeDate::holiday doesn't have Brazil. I therefore used timeDate::Easter to se Carnival and Corpus Christi. 

I also use the weekdays to understand bridges of long weekends.

```{r Creating holiday}
# First on Prophet format
holidays_brazil_prophet <-
  tibble(ds = date(as.character()), weekday = integer(), holiday = as.character(), lower_window = integer(), upper_window = integer()) %>%
  add_row(ds = ymd(timeDate::Easter(YearStart:YearEnd, -2)), holiday = "Easter Friday") %>%
  add_row(ds = ymd(timeDate::Easter(YearStart:YearEnd, -48)), holiday = "Carnival Monday", lower_window = 0, upper_window = 0) %>%
  add_row(ds = ymd(timeDate::Easter(YearStart:YearEnd, -47)), holiday = "Carnival Tuesday", lower_window = 0, upper_window = 0) %>%
  add_row(ds = ymd(timeDate::Easter(YearStart:YearEnd, -46)), holiday = "Carnival Wednesday", lower_window = 0, upper_window = 0) %>%
  add_row(ds = ymd(timeDate::Easter(YearStart:YearEnd, 60)), holiday = "CorpusChristi") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-01-01")), ymd(paste0(YearEnd, "-01-01")), by = "years"), holiday = "New Year's Day") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-01-25")), ymd(paste0(YearEnd, "-01-25")), by = "years"), holiday = "Sao Paulo Anniversary") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-04-21")), ymd(paste0(YearEnd, "-04-21")), by = "years"), holiday = "Tiradentes") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-05-01")), ymd(paste0(YearEnd, "-05-01")), by = "years"), holiday = "Workers' Day") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-09-07")), ymd(paste0(YearEnd, "-09-07")), by = "years"), holiday = "Independece Day") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-10-12")), ymd(paste0(YearEnd, "-10-12")), by = "years"), holiday = "Our Lady of Apparition") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-11-02")), ymd(paste0(YearEnd, "-11-02")), by = "years"), holiday = "All Souls' Day") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-11-15")), ymd(paste0(YearEnd, "-11-15")), by = "years"), holiday = "Republic Day") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-11-20")), ymd(paste0(YearEnd, "-11-20")), by = "years"), holiday = "Black Awareness Day") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-12-24")), ymd(paste0(YearEnd, "-12-24")), by = "years"), holiday = "Christmas Eve") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-12-25")), ymd(paste0(YearEnd, "-12-25")), by = "years"), holiday = "Christmas Day") %>%
  add_row(ds = seq(ymd(paste0(YearStart, "-12-31")), ymd(paste0(YearEnd, "-12-31")), by = "years"), holiday = "New Year's Eve") %>%
  mutate(
    weekday = wday(ds),
    lower_window = ifelse(is.na(lower_window), ifelse(weekday == 3, -1, 0), lower_window),
    upper_window = ifelse(is.na(upper_window), ifelse(weekday == 5, 1, 0), upper_window)
  ) %>%
  arrange(ds)
```

```{r converting holidays to long format}
holidays_brazil <- holidays_brazil_prophet %>%
  dplyr::filter(lower_window != 0 | upper_window != 0) %>%
  mutate(
    ds = (ds + days(upper_window) + days(lower_window)),
    holiday = paste(holiday, " Bridge"),
    lower_window = 0,
    upper_window = 0
  ) %>%
  bind_rows(holidays_brazil_prophet, .) %>%
  select(ds, holiday) %>%
  rename(date = ds) %>%
  distinct(date, .keep_all = TRUE) %>%
  arrange(date) %>%
  mutate(date = as.Date(as.POSIXct(date)))
```

```{r incorporate holidays to data}
data <- data %>%
  mutate(date = date(DateTime)) %>%
  left_join(holidays_brazil, by = c("date" = "date")) %>%
  mutate(holidayflag = ifelse(is.na(holiday), 0, 1)) %>%
  select(-date)

holidays_brazil_prophet <- as_tsibble(holidays_brazil_prophet, index = ds)
```

## Other Features
Besides holidays, I'm activelly adding more variables to the model so we can have more elements to fit a Linear Model (GLM) or Neural Network.
```{r}
data <- data %>%
  tk_augment_timeseries_signature(.date_var = DateTime) %>%
  mutate(daytype = ifelse(wday == 1 | wday == 7, 0, 1)) %>%
  mutate(time = hms::hms(as.numeric(DateTime - floor_date(DateTime, "1 day"), unit = "secs")))
```


## Tsibble & Break Train & Test
```{r}
data_ts <- as_tsibble(data, index = DateTime, key = c("Channel", "Target"))
data_ts_train <- data_ts %>%
  filter_index(. ~ paste(DateCutoff))
data_ts_test <- data_ts %>%
  filter_index(paste(DateCutoff) ~ .)
```

## Future Data
```{r}
ChannelsTargets <- data %>%
  select(Target, Channel) %>%
  distinct(Target, Channel)

data_ts_future <-
  data.frame(DateTime = seq(from = DateEnd + as.duration("15 minutes"), to = DateEnd + as.period(ForecastHorizon), by = as.duration("15 minutes"))) %>%
  mutate(daytype = ifelse(wday(DateTime) == 1 | wday(DateTime) == 7, 0, 1)) %>%
  mutate(time = hms::hms(as.numeric(DateTime - floor_date(DateTime, "1 day"), unit = "secs"))) %>%
  mutate(date = date(DateTime)) %>%
  left_join(holidays_brazil, by = c("date" = "date")) %>%
  mutate(holidayflag = ifelse(is.na(holiday), 0, 1)) %>%
  select(-date) %>%
  tk_augment_timeseries_signature(.date_var = DateTime) %>%
  merge(ChannelsTargets) %>%
  as_tsibble(index = DateTime, key = c("Channel", "Target"))
```

# Modeling Tests
## Prophet
I'm going to evaluate Prophet performance over the train data and one channel.

This way I'll better understand how the model behaves and chose a single model.

```{r}
tictoc::tic()
fit_train_prophet <- data_ts_train %>%
  filter(Channel == "Discovery Channel") %>%
  model(
    pr1 = fable.prophet::prophet(log(ABS + 1) ~ month.lbl + season(period = "week") + season(period = "day") + holiday(holidays_brazil_prophet)),
    pr2 = fable.prophet::prophet(log(ABS + 1) ~ season(period = "week") + season(period = "day") + holiday(holidays_brazil_prophet)),
    pr3 = fable.prophet::prophet(log(ABS + 1) ~ season(period = "week") + season(period = "day"))
  )
tictoc::toc()

accuracy(fit_train_prophet)
```

Observa-se que o modelo mais completo, com dummies de mês, ajusta melhor que os modelos menos completos.

## Fasster
```{r}
future::plan("multiprocess")
tictoc::tic()
fit_train_fasster <- data_ts_train %>%
  filter(
    Channel == "Discovery Channel" # , DateTime >= DateStart + dyears(1)
  ) %>%
  model(
    fasster1 = fasster::FASSTER(log(ABS + 1) ~ trend(1) + fourier(96, 12) + holidayflag),
    fasster2 = fasster::FASSTER(log(ABS + 1) ~ factor(wday) %S% trend(1) + fourier(96, 6) + holidayflag),
    fasster3 = fasster::FASSTER(log(ABS + 1) ~ trend(2) + fourier(96, 6) + fourier(24 * 4 * 7, 6) + holidayflag)
  )
tictoc::toc()

accuracy(fit_train_fasster)
```

A Melhor performamce está no modelo simples,

## TSLM
```{r}
tictoc::tic()
fit_train_tslm <- data_ts_train %>%
  filter(Channel == "Discovery Channel") %>%
  model(
    tslm1 = TSLM(log(ABS + 1) ~ factor(year) + factor(holidayflag) + factor(wday) + factor(month) + factor(time)),
    tslm2 = TSLM(log(ABS + 1) ~ factor(year) + factor(holidayflag) + fourier("week", K = 6) + fourier("day", K = 6)),
  )
tictoc::toc()
accuracy(fit_train_tslm)
```

## Arima
```{r}
tictoc::tic()
fit_train_arima <- data_ts_train %>%
  filter(Channel == "Discovery Channel") %>%
  model(
    arima1 = ARIMA(log(ABS + 1) ~ factor(holidayflag)),
    arima2 = ARIMA(log(ABS + 1) ~ factor(wday) + factor(holidayflag)),
    arima3 = ARIMA(log(ABS + 1) ~ factor(holidayflag) + fourier("week", K = 6) + fourier("day", K = 6))
  )
tictoc::toc()
report(fit_train_arima)
accuracy(fit_train_arima)
```

## ETS
```{r}
tictoc::tic()
fit_train_ets <- data_ts_train %>%
  filter(Channel == "Discovery Channel") %>%
  model(
    ets1 = ETS(log(ABS + 1)),
    # ets2 = ETS(log(ABS + 1) ~ trend(method = c("A", "Ad")) + season(method = c("A", "M"), period = "1 day")) It doesn't work b/c ETS is limited to 24 obs/period and I have 96.
  )
tictoc::toc()
accuracy(fit_train_ets)
glimpse(fit_train_ets)
```
It clearly shows a over-fit issue. 
I'd like to try to run my own Excel ETS algorithm where I do a single model for each weekday. The terms (Alpha, Beta, Phi) are reached through a single log-likelihood function. In my Excel model, I use Solver.


# Final model
```{r}
future::plan("default")
tictoc::tic()
fit_train_prt <- data_ts_train %>%
  model(
    pr1 = fable.prophet::prophet(log(ABS + 1) ~ month.lbl + season(period = "week") + season(period = "day") + holiday(holidays_brazil_prophet)),
    pr2 = fable.prophet::prophet(log(ABS + 1) ~ season(period = "week") + season(period = "day") + holiday(holidays_brazil_prophet))
  )
tictoc::toc()

future::plan("multiprocess")
tictoc::tic()
fit_train_oth <- data_ts_train %>%
  model(
    fasster1 = fasster::FASSTER(log(ABS + 1) ~ trend(1) + fourier(96, 12) + holidayflag),
    fasster3 = fasster::FASSTER(log(ABS + 1) ~ trend(2) + fourier(96, 6) + fourier(24 * 4 * 7, 6) + holidayflag),
    tslm2 = TSLM(log(ABS + 1) ~ factor(year) + factor(holidayflag) + fourier("week", K = 6) + fourier("day", K = 6)),
    arima3 = ARIMA(log(ABS + 1) ~ factor(holidayflag) + fourier("week", K = 6) + fourier("day", K = 6)),
    ets = ETS(log(ABS + 1)),
  )
tictoc::toc()

fit_train <- left_join(fit_train_prt, fit_train_oth, by = c("Channel", "Target"))
```


### Analysis of results
```{r}
fit_train %>%
  accuracy() %>%
  arrange(Channel, MASE)
```

## Forecast Test
```{r}
forecast_test <- fit_train %>%
  select(-tslm2) %>% 
  forecast(data_ts_test)
```

### Analysis of Results
```{r}
accuracy(forecast_test, data_ts_test) %>%
  arrange(Channel, RMSE)
```

# Forecasting
## Modelling with full dataset
```{r}
future::plan("default")
tictoc::tic()
fit <- data_ts %>%
  filter(DateTime >= ymd_hms("2019-01-01 06:00:00", tz = "UTC")) %>% 
  model(
    prophet = fable.prophet::prophet(log(ABS + 1) ~ season(period = "week") + season(period = "day") + holiday(holidays_brazil_prophet))
  ) 

tictoc::toc()
```

## Forecasting
```{r}
forecast <- fit %>%
  forecast(h = "3 months")
```

## Evaluation
```{r}
  forecast %>% 
  filter(DateTime < DateEnd + dweeks(1)) %>% 
  autoplot(filter(data_ts, DateTime >= DateEnd - dweeks(1))) +
  facet_wrap(vars(Channel), ncol = 3, scales = "free")
```


# Export
```{r}
forecast %>%
  # hilo(level = 80) %>%
  # unnest_wider('80%') %>%
  as_tibble() %>%
  select(-.model, -ABS) %>%
  rename(ABS = .mean) %>%
  mutate(Date = date(DateTime),
         Time = substr(as.character(DateTime), nchar(as.character(DateTime)) - (8-1), nchar(as.character(DateTime))),
         ABS = round(ABS,3)
        ) %>% 
  data.table::fwrite(file = "../data_output/forecast.csv", sep = ",", dec = ".")
```
