---
title: "Ratings Forecasting"
date: "`r Sys.Date()`"
output:
  rmdformats::material:
    highlight: kate
---


# Loading Packages and Data Load
## Setup Custom Functions
```{r setup, echo=FALSE, cache=FALSE}

# Custom Functions
  convert.to.sec <- function(X)
  {
    X <- strsplit(X, ":")
    sapply(X, function(Y) sum(as.numeric(Y) * c(3600, 60, 1)))
  }
  
  installpak <- function(pkg){
    new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
    if (length(new.pkg)) 
      install.packages(new.pkg, dependencies = TRUE)
  }

# Load Packages
  RequiredPackages <- c( # Pacotes que uso, mas náo quero carregar, chamo funções de maneira declarada
    "timeSeries" # Usado para criar o calendario (filho do fbasics da família Rmerics)
    ,"data.table" # Uso o fread para importar e fundir as bases
    ,"tictoc" # Controla o tempo 
    ,"remotes" # Instalação dos pacotes do Github
    ,"readr")
  
NonCRANPackages_b <-  c("mitchelloharawild/fable.prophet", "tidyverts/fasster")
remotes::install_github(NonCRANPackages_b)
rm(NonCRANPackages_b)
  
  LoadedPackages <- c(
    "tidyverse" # Life
    ,"skimr"
    ,"future" # Parallel Processing

    #Calendar functions
    ,"lubridate" # Dealing with time (ymd and others)
    ,"timetk" # Exploratory

    #Modeling
    ,"prophet"
    
    #Tidyverts
    ,"tsibble"
    ,"fable"
    ,"feasts"
    ,"fabletools"

    #RMD
    ,"knitr"
    ,"rmdformats")
  
  NonCRANPackages <-  c(
    "fable.prophet" 
    ,"fasster")

installpak(c(RequiredPackages, LoadedPackages))
sapply(c(LoadedPackages, NonCRANPackages), require, character.only = TRUE)

# Global RMarkdown options
  options(max.print="75")
  opts_chunk$set(echo=FALSE,
  	             cache=TRUE,
                 prompt=FALSE,
                 tidy=TRUE,
                 comment=NA,
                 message=FALSE,
                 warning=FALSE)
  opts_knit$set(width=75)

```

## Load TXT Files to the envoriment and tidy data
```{r}
# Load TXT Files to the envoriment ----
data <- readr::read_csv("../data_raw/15minBrazil/Time BTS_Pred_long_20200523_215519.csv",     col_types = cols(Date = col_date(format = "%Y-%m-%d"), Time = col_character()), 
    skip = 2)

# Tidy Data ----
data <- data %>% 
  mutate(DateTime = 
           fast_strptime(as.character(data$Date), "%Y-%m-%d", tz="UTC", lt=FALSE) + 
           seconds(convert.to.sec(data$Time))) %>% 
  select(-Date, -Time, DateTime, Channel = 'Channel Group ...', TRP = 'TRP (avgW)', ABS = "'000 (avg)")
```

# Exploratory
## Seasonal
```{r eval=FALSE, include=FALSE}
data %>%
  mutate(DateTime = ymd_h(paste(date(DateTime),hour(DateTime)))) %>% 
  group_by(DateTime) %>% 
  summarise(ABS = mean(ABS)) %>% 
  plot_seasonal_diagnostics(DateTime, ABS, .feature_set	= c("hour", "wday.lbl", "month.lbl"), .interactive = TRUE)
```

```{r eval=FALSE, include=FALSE}
data_tsble %>% autoplot(ABS)

data_tsble %>% 
    gg_season(ABS, period="day") + theme(legend.position = "none")

data_tsble %>% 
  gg_season(ABS, period="weekday") + theme(legend.position = "none")

data_tsble %>% 
  gg_subseries(ABS, period="year") 

data_tsble %>% 
  features(ABS, feat_stl)


```

# Feature Engineering
## Getting some key aspects
```{r}
DateStart <- min(data$DateTime)
DateEnd <- max(data$DateTime)
DateCutoff <- DateStart + hours(
  round(
    0.9*
      time_length(lubridate::interval(DateStart, DateEnd), "hour"),
    0))
ForecastHorizon <- "6 months"  #Used on final forecast
YearStart <- year(DateStart) #Used on Holidays Tsibble / data.frame
YearEnd <- year(DateEnd + as.duration(ForecastHorizon))  #Used on Holidays Tsibble / data.frame
```

## Holidays
I built the holidays dataset because:
# prophet::generated_holidays doesn't have the ecclesiastical holidays (based on Easter) for Brazil and Proclamation of Republic holiday is on Nov 5th and not on Nov 15. 
# bizdays:holidaysANBIMA doesn't have the name of the holidays, what prevent the creation of dummies for each holiday (effect of "Carnival Tuesday" might be different than the effect of "Christmas Day").
# timeDate::holiday doesn't have Brazil. I therefore used timeDate::Easter to se Carnival and Corpus Christi. 

I also use the weekdays to understand bridges of long weekends.

```{r Creating holiday}
# First on Prophet format
holidays_brazil_prophet <- 
  tibble(ds= date(as.character()), weekday = integer(), holiday= as.character(), lower_window= integer(), upper_window= integer()) %>% 
  add_row(ds = ymd(timeDate::Easter(YearStart:YearEnd,-2)), holiday = "Easter Friday") %>% 
  add_row(ds = ymd(timeDate::Easter(YearStart:YearEnd,-48)), holiday = "Carnival Monday", lower_window = 0, upper_window = 0) %>% 
  add_row(ds = ymd(timeDate::Easter(YearStart:YearEnd,-47)), holiday = "Carnival Tuesday", lower_window = 0, upper_window = 0) %>% 
  add_row(ds = ymd(timeDate::Easter(YearStart:YearEnd,-46)), holiday = "Carnival Wednesday", lower_window = 0, upper_window = 0) %>% 
  add_row(ds = ymd(timeDate::Easter(YearStart:YearEnd,60)), holiday = "CorpusChristi") %>%
  add_row(ds = seq(ymd(paste0(YearStart,"-01-01")), ymd(paste0(YearEnd,"-01-01")), by="years"), holiday = "New Year's Day") %>%
  add_row(ds = seq(ymd(paste0(YearStart,"-01-25")), ymd(paste0(YearEnd,"-01-25")), by="years"), holiday = "Sao Paulo Anniversary") %>%
  add_row(ds = seq(ymd(paste0(YearStart,"-04-21")), ymd(paste0(YearEnd,"-04-21")), by="years"), holiday = "Tiradentes") %>%
  add_row(ds = seq(ymd(paste0(YearStart,"-05-01")), ymd(paste0(YearEnd,"-05-01")), by="years"), holiday = "Workers' Day") %>%
  add_row(ds = seq(ymd(paste0(YearStart,"-09-07")), ymd(paste0(YearEnd,"-09-07")), by="years"), holiday = "Independece Day") %>%
  add_row(ds = seq(ymd(paste0(YearStart,"-10-12")), ymd(paste0(YearEnd,"-10-12")), by="years"), holiday = "Our Lady of Apparition") %>%
  add_row(ds = seq(ymd(paste0(YearStart,"-11-02")), ymd(paste0(YearEnd,"-11-02")), by="years"), holiday = "All Souls' Day") %>%
  add_row(ds = seq(ymd(paste0(YearStart,"-11-15")), ymd(paste0(YearEnd,"-11-15")), by="years"), holiday = "Republic Day") %>%
  add_row(ds = seq(ymd(paste0(YearStart,"-11-20")), ymd(paste0(YearEnd,"-11-20")), by="years"), holiday = "Black Awareness Day") %>%
  add_row(ds = seq(ymd(paste0(YearStart,"-12-24")), ymd(paste0(YearEnd,"-12-24")), by="years"), holiday = "Christmas Eve") %>% 
  add_row(ds = seq(ymd(paste0(YearStart,"-12-25")), ymd(paste0(YearEnd,"-12-25")), by="years"), holiday = "Christmas Day") %>% 
  add_row(ds = seq(ymd(paste0(YearStart,"-12-31")), ymd(paste0(YearEnd,"-12-31")), by="years"), holiday = "New Year's Eve") %>%
  mutate(
    weekday = wday(ds),
    lower_window = ifelse(is.na(lower_window), ifelse(weekday == 3, -1, 0), lower_window), 
    upper_window = ifelse(is.na(upper_window), ifelse(weekday == 5, 1, 0), upper_window)) %>%   
  arrange(ds) 
```

```{r converting holidays to long format}
holidays_brazil <- holidays_brazil_prophet %>% 
  dplyr::filter(lower_window != 0 | upper_window != 0) %>% 
  mutate(ds = (ds + days(upper_window) + days(lower_window)),
         holiday = paste(holiday, " Bridge"),
         lower_window = 0,
         upper_window = 0) %>% 
  bind_rows(holidays_brazil_prophet,.) %>% 
  select(ds, holiday) %>% 
  rename(date = ds) %>% 
  distinct(date, .keep_all = TRUE) %>% 
  arrange(date) %>% 
  mutate(date = as.Date(as.POSIXct(date)))
```

```{r incorporate holidays to data}
data <- data %>% 
  mutate(date = date(DateTime)) %>% 
  left_join(holidays_brazil, by= c("date" = "date")) %>% 
  mutate(holidayflag = ifelse(is.na(holiday), 0, 1)) %>% 
  select(-date)

holidays_brazil_prophet <- as.tsibble(holidays_brazil_prophet)

```

## Timetk Features
Besides holidays, I'm activelly adding more variables to the model so we can have more elements to fit a Linear Model (GLM) or Neural Network.
```{r}
data <- data %>% 
  tk_augment_timeseries_signature(.date_var = DateTime) %>% 
  mutate(daytype = ifelse(wday == 1 | wday == 7, 0, 1))
```


## New Data Dataframe


# Modeling
## Tsibble & Break Train & Test
```{r}
data_tsble <- as_tsibble(data, index=DateTime, key=Channel)
data_train_tsble <- data_tsble %>% 
  filter_index(.~paste(DateCutoff))
data_test_tsble <- data_tsble %>%  
  filter_index(paste(DateCutoff)~.) 
```


## Features
```{r}
NewData <- 
  data.frame(DateTime = seq(from = DateEnd + as.duration('15 minutes'), to = DateEnd + as.period(ForecastHorizon), by = as.duration('15 minutes'))) %>% 
  mutate(wday = wday(DateTime)) %>% 
  mutate(daytype = ifelse(wday == 1 | wday == 7, 0, 1)) %>% 
  mutate(date = date(DateTime)) %>% 
  left_join(holidays_brazil, by= c("date" = "date")) %>% 
  mutate(holidayflag = ifelse(is.na(holiday), 0, 1)) %>% 
  select(-date) %>% 
  tsibble()
```



## Prophet
I'm going to evaluate Prophet performance over the train data and one channel.

This way I'll better understand how the model behaves and chose a single model.

```{r}
tictoc::tic()
fit_train_prophet <- data_train_tsble %>% 
  filter(Channel == "Discovery Channel") %>% 
  model(pr1 = fable.prophet::prophet(log(ABS+1) ~ month.lbl + season(period = "week") + season(period = "day") + holiday(holidays_brazil_prophet)),
        pr2 = fable.prophet::prophet(log(ABS+1) ~ season(period = "week") + season(period = "day") + holiday(holidays_brazil_prophet)),
        pr3 = fable.prophet::prophet(log(ABS+1) ~ season(period = "week") + season(period = "day")))
tictoc::toc()

accuracy(fit_train_prophet)
```

Observa-se que o modelo mais completo, com dummies de mês, ajusta melhor que os modelos menos completos.

## Fasster
```{r}
tictoc::tic()
fit_train_fasster <- data_train_tsble %>% 
  filter(Channel == "Discovery Channel") %>% 
  model(fasster1 = fasster::FASSTER(log(ABS+1) ~ poly(1) + trig(96, 16) + holidayflag + daytype))
tictoc::toc()

accuracy(fit_train_fasster)
```

## Arima
```{r}
tictoc::tic()
fit_train_other <- data_train_tsble %>% 
  filter(Channel == "Discovery Channel") %>% 
  model(arima1 = ARIMA(log(ABS+1) ~ factor(holidayflag)))
tictoc::toc()
accuracy(fit_train_other)

```

```{r}

temp <- fit_train_other %>% 
  select(arima) %>% 
  report()

```





### Analysis of results
```{r}
fit_train %>%
  accuracy() %>%
  arrange(Channel, MASE)
```

## Forecast Test
```{r}
forecast_test <- fit_train %>% 
  select(-glm) %>% 
  forecast(data_test_tsble)
```

### Analysis of Results
```{r}
accuracy(forecast_test, data_test_tsble) %>% 
  arrange(Channel, MASE)
```

# Forecasting
## Modelling with full dataset
```{r}
tictoc::tic()
future::plan("multiprocess") # Não adianta muito porque o Prophet não paralelilza
fit <- data_tsble %>% 
  select(-TRP) %>% 
  model(
    prophet = fable.prophet::prophet(log(ABS+1) ~ season(period = "week") + season(period = "day") + holiday(holidays_brazil_prophet))) 
tictoc::toc()
```

## Forecasting
```{r}
forecast <- fit %>% 
  forecast(h="3 months")
```


# Export
```{r}
forecast %>% 
  #hilo(level = 80) %>% 
  #unnest_wider('80%') %>% 
  as_tibble() %>% 
  select(-.model, -.distribution) %>% 
  mutate(ABS = round(ABS, 3)) %>% 
  data.table::fwrite(file = "forecast.csv", sep=",", dec = ".")
```



